So you want to add a new standard to the Ingalls Standards Sheet!

Please run the below chunks one at a time.


```{r Load data, include=TRUE}
library(httr) 
library(tidyverse)
```

Please enter the name of the new standared:
```{r Compound_Name, include=TRUE}
New_Compound_Name <- "Inosine"
```

Run this chunk to retrieve the KEGG code and KEGG names:
```{r Add KEGG, include=TRUE}
KEGG_Database <- read.csv(dir("data_extra", full.names=T, pattern="KEGG_Download"))

FindKEGGCode <- function(Compound_Name) {
  path <- "http://rest.kegg.jp/list/compound"
  raw_content <- GET(url = path) %>%
    content()

  All_KEGG_IDs <- read.csv(text = gsub("\t\n", "", raw_content), sep = "\t",
                           header = FALSE, col.names = c("cmpd", "name"))

  Search_Results <- All_KEGG_IDs %>%
    separate_rows(name, sep = ";") %>%
    mutate(name = str_trim(name, side = "both")) %>%
    filter(str_detect(name, str_c(New_Compound_Name, collapse = "|"))) 
  
 return(Search_Results) 
}

KEGG_Results <- FindKEGGCode(New_Compound_Name)
```

Enter the KEGG code from the above step.
Run this chunk to get the ChEBI info:
```{r Add ChEBI, include=TRUE}

KEGG_Code <- "cpd:C00294"

FindChEBICode <- function(KEGG_Code) {
  # Accepts a KEGG ID (format cpd:C[number]) and returns
  # the ChEBI id found on the KEGG webpage. If there are multiple, return the
  # first one. If not found, return NA.
  if(is.na(KEGG_Code)) {
    return(NA)
  }
  ChEBI <- KEGG_Code %>%
    paste0("http://rest.kegg.jp/get/", .) %>%
    GET() %>%
    content() %>%
    as.character() %>%
    strsplit(., "\\n") %>%
    unlist() %>%
    grep(pattern = "ChEBI", value = TRUE) %>%
    trimws(which = "both")
  ChEBI <- sub("^(\\S*\\s+\\S+).*", "\\1", ChEBI)
  ChEBI <- gsub( " ", "", ChEBI)
  if(length(ChEBI) == 0) {
    return(NA)
  }
  return(ChEBI)
}

ChEBI_Results <- FindChEBICode(KEGG_Code = KEGG_Code)

```

Run this chunk for PubChem, InCHI and SMILES codes.
```{r Test Standards, include=TRUE}

## Doing this with one specific compound
FindPubChemCodes <- function(Compound_Name) {
  path <- paste("https://pubchem.ncbi.nlm.nih.gov/rest/pug/compound/name/", New_Compound_Name,
                "/property/Title,MolecularFormula,inchikey,CanonicalSMILES,IUPACName/CSV", sep = "")
  
  r <- GET(url = path)
  status_code(r)
  content(r, encoding = "UTF-8")
  PubChemData <- read.csv(text = gsub("\t\n", "", r), sep = ",",
                     header = TRUE) %>%
    rename(Compound_Name = Title,
           InChI_Key_Code = InChIKey,
           Canon_SMILES_Code = CanonicalSMILES,
           IUPAC_Code = IUPACName,
           PubChem_Code = CID,
           PubChem_Formula = MolecularFormula) %>%
    select(PubChem_Code, Compound_Name, InChI_Key_Code:IUPAC_Code)
  
  return(PubChemData)
}

PubChem_Results <- FindPubChemCodes(New_Compound_Name)

```

Run this chunk to add the Classyfire classification
```{r Classyfire, include=TRUE}

FindClassyfire <- function(PubChem) {
  
  source("src/High_Class_Function_062220.R")
  
  myinput <- PubChem %>%
    select(Compound_Name, InChI_Key_Code)
  
  Classyfire <- high_class(myinput)
  
  Combined_Classyfire <- Classyfire %>%
    unite(Combined, c("Level", "Classification"), sep = ": ") %>%
    arrange(key) %>%
    group_by(key) %>%
    mutate("Classyfire" = paste(Combined, collapse = "; ")) %>%
    select(-Combined, - CHEMONT) %>%
    unique() %>%
    as.data.frame()
  
  return(Combined_Classyfire)
}

Classyfire_Results <- FindClassyfire(PubChem_Results)
```

