---
title: "Ingalls Standards Project: Structural Changes"
author: "R.Lionheart"
date: "Start date: 3/17/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
library(httr) 
library(stringr)
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)

```

## This markdown document controls the original large structural changes made in 2020. 

#### Change Log
4/8/20: Internal standards updated to reflect consistent naming scheme.  
4/20/20: Abbreviated compounds switched to full-length KEGG names.  
4/20/20: Adjusted compounds with incorrect capitalization.  
4/22/20: Added or removed symbols as required by KEGG names.  
4/23/20: Update last compounds not falling into the above groups.
4/23/20: Complete renaming of compounds, including those that didn't change from the original names.
4/28/20: Adjust vitamins to descriptive names.
4/29/20: Adjust abbreviations for consistency.
5/8/20: FINAL NAMES DECIDED FOR PRIMARY ID.
5/28/20: Bug fixes in final names.
5/28/20: First suggestions for Figure Name column.
6/3/20: Final Figure Names decided.
7/30/20: ChEBI names scraped from website and added in new column.
8/3/20: IUPAC, InCHI, and SMILES columns added to standards.
8/10/20: Classyfire classifications added for those compounds that have them.
10/14/20: First version of SQL-safe names introduced. 
10/22/20: Remove all trailing numbers from SQL-safe names. This is the column to be used for CMAP.
------

## IMPORTANT: PLEASE READ
The below code blocks represent **the order** in which large structural changes were made. Running these code blocks *WILL NOT* replace any of the Ingalls_Standards sheets. They exist only as a reference for troubleshooting. 

#### Primary ID (column: Compound_Name)
```{r Primary ID code, include=TRUE}
source("src/Primary_ID.R")

rm(list=setdiff(ls(), "Ingalls_Lab_Standards_PrimaryID"))
```

#### Shortened names (column: Compound_Name.figure)
```{r Figures Names code, include=TRUE}
source("src/Figure_Names.R")

rm(list=setdiff(ls(), "Ingalls_Lab_Standards_FigNames"))

```

-----

# KEGG stuff will prolly go here

#### ChEBI and KEGG columns
```{r ChEBI code, include=TRUE}
source("src/CHEBI_check.R")

#Ingalls_Lab_Standards_ChEBI <- read.csv("data_extra/TEMPCHEBI.csv")
```

-----

#### IUPAC, InCHl, SMILES columns
```{r IUPAC, InCHI, and SMILES code, include=TRUE}
source("src/IUPAC_InChl_Smiles.R")
```

-----

The next section deals with the ClassyFire ID section. 
The source code for creating the ClassyFire IDs commented out: *DO NOT RUN THE High Class Function LINE UNLESS YOU ARE STARTING THE PROJECT FROM SCRATCH!!* It can take several hours just to complete.

#### Classyfire column
```{r Source Classyfire code, include=TRUE}
### source("src/High_Class_Function_062220.R") ###
source("src/Classyfire.R")
```

-----

#### SQL-safe names: no special characters or leading numbers.
```{r Source SQL-Safe code, include=TRUE}
source("src/SQL_Safe.R")
```

