---
title: "Ingalls Standards Project: Structural Changes"
author: "R.Lionheart"
date: "Start date: 3/17/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
library(httr) 
library(stringr)
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```

## IMPORTANT: PLEASE READ
The below code blocks represent **the order** in which large structural changes were made. Running these code blocks *WILL NOT* replace or modify the Ingalls_Standards sheet. They exist only as a reference for troubleshooting and as a guideline for future structural changes.

### This markdown document controls both the original large structural changes made in 2020, and the revamp completed in the summer of 2021.

------

Load pre-2021 Standards sheet, located in the data_old/ directory.

```{r Load old standards, include=TRUE}
Ingalls_Lab_Standards <- read.csv("data_old/Ingalls_Lab_Standards_August2021.csv")
```

------

#### Primary ID (column: Compound.Name)

The Primary ID column was adjusted back in 2020. This involved two parts: one redo by Laura followed by a joint tidying by Regina and Laura. 
To see the original, pre-primary ID revamp, please take a look at the  data_old/Ingalls_Lab_Standards_pre2020.csv.
To see Laura's edits from 2020, go to data_old/Ingalls_Lab_Standards_LauraEdit2020.csv.
The rest of the changes are all outlined in the src/Primary_ID.R script below.

```{r Primary ID code, include=TRUE}
source("src/Primary_ID.R")

rm(list=setdiff(ls(), "Ingalls_Lab_Standards_PrimaryID"))
```

-----

#### Figure Names (column: Compound.Name_figure)

This script handles the creation of the Figure Names column: shorter names for the compounds. The script shows how changes were made, as well as a record of all names that had to be changed manually.

```{r Figures Names code, include=TRUE}
source("src/Figure_Names.R")

rm(list=setdiff(ls(), "Ingalls_Lab_Standards_FigNames"))
```

-----

#### SQL-safe names (column: Compound.Name_SQL)

This script deals with the creation of the SQL names column. This columnn is for uploading compounds into online databases that require consistency, and sometimes requires that entries contain no special characters or leading numbers.

```{r Source SQL-Safe code, include=TRUE}
source("src/SQL_Safe.R")

rm(list=setdiff(ls(), "Ingalls_Lab_Standards_SQL"))
```

-----

#### KEGG (columns: KEGG_Code, KEGG_Names)

This section relies on accessing the remote KEGG database to update the codes and names. These values don't change often and running this chunk can take quite a while. If you want to scrape KEGG and save the latest version, uncomment the chunk below and run it.

Alternatively, use the latest downloaded version, located at data_extra/KEGG_Download_<Latest_Date_Here>.csv.

Option 1: Pull down latest data from KEGG (only run if you want the absolute latest version).
This also includes saving the latest scrape to the data_extra folder.

```{r Scrape KEGG code, include=TRUE}
# path <- "http://rest.kegg.jp/list/compound"
# raw_content <- GET(url = path) %>%
#   content() 
#   
# All_KEGG_IDs <- read.csv(text = gsub("\t\n", "", raw_content), sep = "\t",
#               header = FALSE, col.names = c("cmpd", "name"))
# write.csv(All_KEGG_IDs, paste0("data_extra/KEGG_Download_",
#                                format(Sys.time(), "%d-%b-%Y"), ".csv"),
#           row.names = FALSE)
```

Option 2: load a pre-saved KEGG scrape. The date in the filename indicates when it was last downloaded. You will need to enter the filename correctly for the My_KEGG_File variable, as there may be more than one downloaded KEGG files.
```{r Load prescraped KEGG, include=TRUE}
My_KEGG_File <- "KEGG_Download_03-Aug-2021"
All_KEGG_IDs <- read.csv(dir("data_extra/", full.names = T, pattern = My_KEGG_File))
```


Run the KEGG script to update the standards.
```{r Run KEGG script}
source("src/KEGG.R")

rm(list=setdiff(ls(), "Ingalls_Lab_Standards_KEGG"))
```

-----

#### ChEBI (column: ChEBI_Code)

Like the KEGG section, this section handles downloading and updating the ChEBI codes. 
Downloading ChEBI takes time; if you don't want to do the update you can skip this chunk and use the latest downloaded version, located at data_extra/ChEBI_Download_<Latest_Date_Here>.csv.
```{r Download latest ChEBI, include=TRUE}
# source("src/ChEBI_Download.R")
# 
# ## Save the standards sheet with the latest ChEBI download here.
# write.csv(Latest_ChEBI_Download, paste0("data_extra/ChEBI_Download_",
#                                       format(Sys.time(), "%d-%b-%Y"), ".csv"),
#           row.names = FALSE)
```

This section is for using the latest downloaded ChEBI file and updating the standards sheet.
Remember you need to enter the exact filename of the last download.
```{r Last updated ChEBI, include=TRUE}
# Load the latest ChEBI scrape if you don't want to run the whole function.
My_ChEBI_File <- "ChEBI_Download_05-Aug-2021"
Full_ChEBI <- read.csv(dir("data_extra/", full.names=T, pattern = My_ChEBI_File))
```

This section runs the downloaded ChEBI data and updates the Ingalls Standards.
It drops the old CheBI column and prints differences between the two. 
```{r Run ChEBI, include=TRUE}
source("src/ChEBI.R")

rm(list=setdiff(ls(), "Ingalls_Lab_Standards_ChEBI"))
```

-----

#### IUPAC, InCHl, SMILES (columns: IUPAC_Code, InCHI_Key_Code, Canon_SMILES_Code)

As with KEGG and ChEBI, the section below downloads the IUPAC, INCHI, and SMILES columns from the remote PubChem database, and takes a few minutes to run. You can either run the chunk to get the latest data, or use a previously downloaded version, located at data_extra/PubChem_Download_<Latest_Date_Here>.csv.
```{r PubChem download code, include=TRUE}
# source("src/PubChem_Download.R")
# 
# write.csv(All_PubChem_Data, paste0("data_extra/PubChem_Download_",
#                                    format(Sys.time(), "%d-%b-%Y"), ".csv"),
#           row.names = FALSE)
```

Run this chunk to use the last updated PubChem file. Remember to enter the correct filename for the latest download.
```{r Last updated PubChem, include=TRUE}
My_PubChem_File <- "PubChem_Download_04-Aug-2021"
Full_PubChem <- read.csv(dir("data_extra/", full.names=T, pattern = My_PubChem_File))
```

Update all Pubchem data.
```{r Add all PubChem code, include=TRUE}
source("src/PubChem.R")

rm(list=setdiff(ls(), "Ingalls_Lab_Standards_AllPubChem"))
```

-----

The next section deals with the ClassyFire ID section. 

*DO NOT RUN THE High Class Function LINE UNLESS YOU WOULD LIKE TO COMPLETELY UPDATE IT!*  

Like the other remote downloads, the Classyfire script is commented out. *Unlike* the other scrapes, which take ~5 mins, the Classyfire one takes up to several hours.

#### Classyfire (column: Classyfire)

```{r Source Classyfire code, include=TRUE}
# source("src/High_Class_Function_062220.R")
# source("src/Classyfire_Download.R")
# 
# write.csv(Combined_Classyfire, paste0("data_extra/Classyfire_Download_",
#                                    format(Sys.time(), "%d-%b-%Y"), ".csv"),
#           row.names = FALSE)
```

Use a downloaded Classyfire run
```{r Update the Classyfire column, include=TRUE}
My_Classyfire_File <- "Classyfire_Download_04-Aug-2021"
Full_Classyfire <- read.csv(dir("data_extra/", full.names=T, pattern = My_Classyfire_File))

source("src/Classyfire.R")

rm(list=setdiff(ls(), "Ingalls_Lab_Standards_Classyfire"))
```

----

#### Standards Facelift

This section handles the layout changes for the standards sheet; including column removal/addition, column order.

```{r Standards Facelift, include=TRUE}
source("src/Standards_Facelift.R")
```

----

#### Replace deuterized Empirical_Formula

This section handles replacing all internal standards "D"s with "H(2)"s. 

```{r Replace deuterization, include=TRUE}
source("src/EmpiricalDeuterize.R")
```



